%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
{\Huge \scshape Shaswat Gupta} \\ \vspace{1pt}
Zurich, Switzerland \\ \vspace{1pt}
\small \raisebox{-0.1\height}\faEnvelope\ \href{mailto:shagupta@ethz.ch}{\underline{Email}} ~ 
\href{https://linkedin.com/in/shaswat-gupta/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
\href{https://github.com/Shaswat-G}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} ~
\href{https://shaswat.dev}{\raisebox{-0.2\height}\faGlobe\ \underline{shaswat.dev}}
\vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ETH Zürich}{Sept 2023 -- Present}
      {MSc Computer Science, Machine Intelligence \& Data Management Systems, GPA: 5.25/6}{Zurich, Switzerland}
    \resumeSubheading
      {Indian Institute of Technology Bombay (IIT Bombay)}{July 2018 -- Aug 2022}
      {B.Tech in Mechanical Engineering, Rank 1, Gold Medalist, GPA: 9.6/10}{Mumbai, India}
  \resumeSubHeadingListEnd

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     \begin{multicols}{4}
%         \begin{itemize}[itemsep=-5pt, parsep=3pt]
%             \item\small Large Scale AI Engineering
%             \item Cloud Computing Architecture
%             \item Big Data
%             \item Machine Learning
%             \item Deep Learning
%             \item Machine Perception
%             \item Computational Intelligence Lab
%             \item System Security
%         \end{itemize}
%     \end{multicols}
%     \vspace*{2.0\multicolsep}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart


    \resumeSubheading
      {AB InBev — Growth Analytics Center}{Aug 2022 -- Aug 2023}
      {}{Bangalore, India}
      \vspace{-15 pt}
      \resumeSubSubheading{Full Stack Data Scientist (full-time, 6 months)}{}
      \resumeItemListStart
        \resumeItem{Led US supply chain optimization delivering \$2.4M annual savings through ensemble forecasting and logistics optimization.}
        \resumeItem{Rapidly promoted in 6 months; received prestigious 'Pitcher' Award for Global Impact among 200+ employees.}
      \resumeItemListEnd
      
      \resumeSubSubheading{Associate ML Engineer (full-time, 6 months)}{}
      \resumeItemListStart
        \resumeItem{Engineered end-to-end ML solutions for 2,000+ US distribution routes; earned 'Pint' Award for Exceptional Performance.}
        \resumeItem{Built production-grade forecasting pipeline and Gurobi-powered integer programming optimizer for logistics.}
      \resumeItemListEnd

      \resumeSubSubheading{Data Science \& ML (internship, 2 months)}{May 2021 -- Jul 2021}
      \resumeItemListStart
          \resumeItem{Developed ML-powered product recommendation engine using SVD/NMF algorithms, driving \$6M  annual revenue growth}
        \resumeItem{Outperformed existing models by 30\%, Awarded Best Intern among 100+ peers; received full-time Associate ML Engineer offer.}
      \resumeItemListEnd

    % \resumeSubheading
    % {World Bank Group × KPMG India}{Apr 2021 -- May 2021}
    % {Summer Associate}{Mumbai, India}
    %     \resumeItemListStart
    %       \resumeItem{Spearheaded strategic research, quantitative analysis \& 10-year demand forecasting models for key industries across three nations}
    %       % \resumeItem{Created market readiness framework by synthesizing energy policies and sustainability commitments across emerging economies.}
    %       \resumeItem{Conducted comparative economic modeling of conventional fuels against alternatives; assessment cited in multiple publications.}
    %       % \resumeItem{\textbf{Tech:} Quantitative Research, Statistical Modeling, Data Visualization, Economic Analysis, Python.}
    %     \resumeItemListEnd

    \resumeSubheading
              {Growth Source Financial Technologies (Protium)}{Apr 2020 -- Jul 2020}
              {Data Science (internship, 2 months)}{Mumbai, India}
      \resumeItemListStart
          \resumeItem{Engineered combinatorial optimization model for MSME debt portfolios and an AI-driven loan recommendation engine}
          % \resumeItem{Implemented sales territory optimization using geospatial analytics with Google Maps API and K-means clustering.}
          \resumeItem{Built automated pipeline for time-based yield analysis across 600+ debt securities; received partner-signed recommendation.}
          % \resumeItem{\textbf{Tech:} Python, PuLP, NumPy, Pandas, scikit-learn, Google Maps API, AWS, Apache Spark, Statistical Modeling.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart
        \resumeSubheading
      {Institute for Machine Learning, ETH Zürich}{Jan 2024 -- Present}
      {Research Projects}{Zurich, Switzerland}
            \resumeItemListStart
                \resumeItem{\textbf{Large Scale AI Engineering:} Engineered PyRecover module for distributed checkpointing and auto job resubmission in distributed GPU training. Significantly improved fault tolerance across HPC clusters and reduced compute waste}
                \resumeItem{\textbf{SimpleSleepNet:} Developed lightweight self-supervised framework for EEG-based sleep stage classification (80\%+ accuracy, $<$1MB model). Evaluated 13 signal augmentations and designed modular pretraining framework reducing annotation needs}
                \resumeItem{\textbf{DeepSleepBench:} Benchmarked self-supervised pre-training paradigms (Contrastive, Masked, Hybrid) for EEG signals across neural architectures. Engineered latent space quality metrics, establishing CNN+Attention with contrastive objectives as optimal}
            \resumeItemListEnd

        \resumeSubheading
      {Chair of Technology and Innovation Management, ETH Zürich}{Mar 2024 -- Present}
      {Research Assistant supervised by Prof. Dr. Stefano Brusoni}{Zurich, Switzerland}
            \resumeItemListStart
                \resumeItem{\textbf{Enterprise ML/AI Adoption Research:} Designed data pipeline and statistical analysis framework for 600+ enterprises. Automated 10,000+ statistical tests with dynamic visualization, reducing analysis time by 80\%. \textit{Python, scipy, OpenAI API}.}
                \resumeItem{\textbf{Unicode Technical Standards Analysis:} Built document crawlers and classifiers achieving 96\% accuracy across 30+ categories. Engineered parallel keyword extraction and optimized LLM integration \textit{Python, BeautifulSoup4, NLTK, concurrent.futures}.}
                \resumeItem{\textbf{Semiconductor Patent Analysis:} Developed asyncio-powered data acquisition system (20× faster) and BERTopic modeling identifying 80+ technology clusters. Visualized technological shifts across 40+ years. \textit{Python, BERTopic, HDBSCAN, PyTorch}.}
      \resumeItemListEnd

    \resumeSubheading
      {Industry Research Projects}{2019 -- 2021}
      {Research Associate}{India}
      \resumeItemListStart
        \resumeItem{\textbf{World Bank Energy Strategy:} Spearheaded quantitative analysis and 10-year demand forecasting across three nations. Developed comparative assessment of conventional fuels against clean alternatives and created market readiness framework synthesizing energy policies. \textit{Economic Modeling, Statistical Modeling, Quantitative Analytics}.}
        \resumeItem{\textbf{ISB Epidemiological Modeling:} Conducted advanced modeling with Prof. Sarang Deo analyzing grain movement across 3,200+ agricultural markets serving 12,800+ villages during COVID-19. Implemented polynomial regression and adapted SIR models to forecast transmission patterns. \textit{Python, Geospatial Analysis, Statistical Modeling}.}
        \resumeItem{\textbf{Generative AI - Synthetic Media:} Contributed to Forbes 30-Under-30 startup RephraseAI (acquired by Adobe) developing AI-generated synthetic video technology. Presented at AWS AI Conclave to 100+ CXOs, designed feature validation with 160+ Mechanical Turk respondents. \textit{Generative AI, NLP, Deep Learning, AWS}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------HONORS & SKILLS-----------
\section{Honors \& Skills}
\begin{multicols}{2}

% Left column - Awards
\subsection*{Awards \& Distinctions}
\begin{itemize}[leftmargin=0.15in]
    \item \textbf{Gold Medalist \& Department Rank 1}, IIT Bombay (2022)\\
          Highest CGPA in Mechanical Engineering class of 165 students
    \item \textbf{Institute Academic Award}, IIT Bombay (2021)\\
          Awarded to top 2 students for highest grade points of academic year
    \item \textbf{AB InBev 'Pitcher' \& 'Pint' Awards} (2023)\\
          Recognition for global impact and exceptional performance
    \item \textbf{IIT Bombay Journalism Color Award} (2022)\\
          Institute's most prestigious journalism honor (2 of 10,000+ students)
    \item \textbf{OPJEMS Scholarship}, Jindal Group (2021)\\
          Selected among 3 of 1100+ entrepreneurial students
    \item \textbf{Mensa International Member} (2025)\\
          High IQ society membership, India chapter
    \item \textbf{KC Mahindra Scholarship} for ETH Zurich (2023)
    \item \textbf{Heyning-Roelli Scholarship}, ETH Zurich (2022)
\end{itemize}

\columnbreak

% Right column - Skills
\subsection*{Technical Skills}
\begin{itemize}[leftmargin=0.15in]
    \item \textbf{Programming}\\
          Python, SQL, Bash/Linux, C/C++ (CUDA), R
    \item \textbf{Machine Learning \& AI}\\
          PyTorch, TensorFlow, scikit-learn, XGBoost, Hugging Face Transformers, LLMs, OpenAI API
    \item \textbf{Data Engineering}\\
          Pandas, NumPy, PySpark, Snowflake, PostgreSQL, BigQuery
    \item \textbf{MLOps \& Cloud}\\
          Docker, Kubernetes, AWS, Azure, GitHub Actions, MLflow, Weights \& Biases
    \item \textbf{Optimization \& Algorithms}\\
          Gurobi, PuLP, OR-Tools, Linear/Integer Programming, SLURM, concurrent processing
    \item \textbf{Time Series \& Forecasting}\\
          ARIMA/SARIMAX, Prophet, Ensemble methods
    \item \textbf{Visualization \& Development}\\
          Plotly, Tableau, Git, FastAPI
\end{itemize}

\end{multicols}



  
\vspace{-16pt}

%-----------AWARDS-----------
% \section{Awards}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Department Rank 1 \& Gold Medalist, IIT Bombay}{2022}
%       {Highest CGPA in 2022 class of B.Tech Mechanical Engineering}{}
%     \resumeSubheading
%       {KC Mahindra Scholarship}{July 2023}
%       {Prestigious scholarship for graduate studies abroad (ETH Zurich)}{}
%     \resumeSubheading
%       {Institute Academic Award, IIT Bombay}{2021}
%       {Top 2 students for highest grade point scores of the year}{}
%     \resumeSubheading
%       {Heyning-Roelli Scholarship, ETH Zurich}{Feb 2022}
%       {Merit and need-based international exchange scholarship}{}
%     \resumeSubheading
%       {Mensa International High IQ Society}{April 2025}
%       {Member, Mensa India chapter}{}
%   \resumeSubHeadingListEnd
% \vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
% \section{Technical Skills}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Programming:} Python (ML/Data), SQL (Snowflake/Postgres), Bash/Linux, C/C++, R, JavaScript/TypeScript \\
%      \textbf{ML/AI:} PyTorch, TensorFlow, scikit-learn, XGBoost, LightGBM, Prophet, BERTopic, HuggingFace, OpenAI API \\
%      \textbf{Data Engineering:} Pandas, NumPy, Polars, PySpark, PyArrow, DuckDB, Snowflake, PostgreSQL, BigQuery \\
%      \textbf{MLOps/Cloud:} MLflow, W\&B, Docker, Kubernetes, AWS, Azure, GitHub Actions, Airflow \\
%      \textbf{Optimization:} Gurobi, PuLP, OR-Tools, Linear/Integer Programming \\
%      \textbf{Visualization:} Plotly, Matplotlib, Seaborn, Tableau \\
%      \textbf{Other:} GeoPandas, BeautifulSoup, FastAPI, Git, LaTeX, JupyterLab, VS Code
%     }}
%  \end{itemize}
%  \vspace{-16pt}

%-----------EXTRACURRICULARS-----------
% \section{Extracurriculars \& Leadership}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Editor, Student Journalism Wing (Insight), IIT Bombay}{2019 -- 2022}
%       {Led 200+ student journalists, published author at ETH D-INFK's Visionen magazine}{}
%       \resumeItemListStart
%         \resumeItem{Published 18+ articles reaching 60,000+ alumni; led official campus publication for 10,000+ community.}
%       \resumeItemListEnd
%     \resumeSubheading
%       {Project Leader, Data Analytics Team, IIT Bombay}{2020 -- 2022}
%       {Published institute-level reports on graduate admissions and COVID-19 impact; developed interactive dashboards}{}
%     \resumeSubheading
%       {Mentorship \& Community}{2019 -- Present}
%       {Guided 70+ AB-InBev interns; mentored ETH Zurich undergraduates; led NSS sustainability teaching}{}
%     \resumeSubheading
%       {Communication \& Public Speaking}{2018 -- Present}
%       {Interviewed startup CEOs; secured 3rd in Debating Championship; organized cultural showcases in Zurich}{}
%   \resumeSubHeadingListEnd

\end{document}